---
title: "Summary of UF Titles of Interest"
author: "Philip Chase"
date: "12/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  knitr
)
```

```{r get_data, include=FALSE}
emp_input_file <- "input/emp.csv"
if (!file.exists(emp_input_file)) download.file("https://prod.flbog.net:4445/pls/apex/f?p=140:30:", emp_input_file)
```

```{r read, include=FALSE}
col_types <- cols(
  University = col_character(),
  `Budget Entity` = col_character(),
  `Position Number` = col_character(),
  `Last Name` = col_character(),
  `First Name` = col_character(),
  MI = col_character(),
  `Employee Type` = col_character(),
  FTE = col_double(),
  `Class Code` = col_character(),
  `Class Title` = col_character(),
  `Annual Salary` = col_double(),
  `OPS Term Amount` = col_double()
)

emp <- read_csv(emp_input_file, col_types = col_types)

```


```{r titles, echo=FALSE}
all_titles <- emp %>%
  filter(University == "UF") %>%
  distinct(`Class Title`)

View(all_titles)

View(all_titles %>% 
  filter(str_detect(`Class Title`, str_to_upper("web"))))

```
# Summary Stats for Annualized Salaries

The titles included here are a subset of the titles in use at the University of Florida. These titles were of particular interest to my team when we I wrote this report.

The data shown here sum and annualize the salaries from different funding sources by `Position Number` and `Class Title`. For example, if Jane Doe works 3/4 time as an Application Developer Analyst IV with funding from two different sources at $25,000 and $50,000, those records will be summarized into one record for Jane working 3/4 time for $75,000/year. From that data her _Annualized Salary_ will be computed as salary/FTE = $75,000/0.75 = $100,000. It is this _annualized salary_ from which we compute the summary statistics. 

These stats are valid for estimating fair pay for time worked. They are _not_ suitable for estimating the cost of these titles to UF. 

```{r summarise, echo=FALSE}

titles <- c("APPLIC DEVELOPER ANALYST I", "APPLIC DEVELOPER ANALYST II", "APPLIC DEVELOPER ANALYST III",
            "APPLIC DEVELOPER ANALYST IV", "APPLIC DEVELOPER ANALYST V",
            "DATA MANAGEMENT ANALYST I", "DATA MANAGEMENT ANALYST II", "DATA MANAGEMENT ANALYST III",
            "BUSINESS RELATIONSHIP MGR I", "BUSINESS RELATIONSHIP MGR II", "BUSINESS RELATIONSHIP MGR III",
            "IT MANAGER", "IT TRAINING SPECIALIST", "MGR, IT", "ASO DIR, IT", "DIR, IT",
            "EDUCATION/TRAINING SPEC I", "EDUCATION/TRAINING SPEC II", "EDUCATION/TRAINING SPEC III",
            "SYSTEMS ADMIN/PROGRAMMER III",
            "SYSTEMS ADMIN/PROGRAMMER IV",
            "SYSTEMS ADMIN/PROGRAMMER V",
            "SYSTEMS ADMIN/PROGRAMMER I",
            "SYSTEMS ADMIN/PROGRAMMER II",
            "WEB DESIGNER I",
            "WEB DESIGNER II",
            "WEB DEVELOPER I",
            "WEB DEVELOPER II",
            "WEB DEVELOPER III"
            )
summary_stats_by_title <- emp %>%
  filter(University == "UF") %>%
  filter(`Class Title` %in% titles) %>%
  group_by(`Budget Entity`, `Position Number`, `Last Name`, `First Name`, `Class Title`) %>%
  summarise(salary = sum(`Annual Salary`), fte = sum(FTE)) %>%
  mutate(annualized_salary = salary/fte) %>%
  group_by(`Class Title`) %>%
  summarise(Count = n(), Maximum = round(max(annualized_salary)), 
            `Quartile 3` = round(quantile(annualized_salary)[[4]]),
            Mean = round(mean(annualized_salary)), 
            Median = round(median(annualized_salary)), 
            `Quartile 1` = round(quantile(annualized_salary)[[2]]), 
            Minimum = round(min(annualized_salary)))

View(summary_stats_by_title)
kable(summary_stats_by_title, caption = "Summary statistics of annualized salaries for select titles")
```
